Estimating Correspondences of Deformable Objects ``In-the-wild"

### 2015-11-06 contents/implementation.tex
Updates from ShareLaTeX

SVMs with RBF kernel function map any number of data points onto an infinite-dimensional space where positive and negative points are linearly separable, hence the classification boundary on 2D space represents the actual shape of the object. Note that the decision function for SVMs can be mathematically expressed as:
\begin{equation} \label{eq:decisionfunc}
    d(\bm{x})=\sum_i\alpha_i \, k(\bm{x}_i^*,\bm{x})
\end{equation}
where $\bm{x}_i^*$ are the so-called support vectors and \mbox{$k(\bm{x}, \bm{y}) = \exp\left(-\frac{\|\bm{x} -\bm{y}\|^2}{2 \sigma^2}\right)$} is the RBF kernel. The decision function $d(\bm{x})$ can be defined for every pixel $\bm{x}$ of the corresponding object image, therefore we interpret is as an image and we call it \emph{SVS image}.

@@

\subsubsection{Non-rigid ICP and Correspondence Basis Creation} \label{sec:trabasis}

@@

\subsubsection{Variational Shape Flow Estimation}%{Multi-image Subspace Flow}
\label{varshapeflow}

@@

Figure~\ref{fig:deformationfield} shows some examples of deformation fields derived from the estimated shape flow computed by the aforementioned method. These results correspond to exemplar training shapes in the case of a face dataset.

@@

>>>>

SVMs with RBF kernel function map any number of data points onto an infinite-dimensional space where positive and negative points are linearly separable, hence the classification boundary on 2D space represents the actual shape of the object. Note that the decision function for SVMs can be mathematically expressed as:
\begin{equation} \label{eq:decisionfunc}
    d(\bm{x})=\sum_i\alpha_i \, k(\bm{x}_i^*,\bm{x})
\end{equation}
where $\bm{x}_i^*$ are the so-called support vectors and \mbox{$k(\bm{x}, \bm{y}) = \exp\left(-\frac{\|\bm{x} -\bm{y}\|^2}{2 \sigma^2}\right)$} is the RBF kernel. The decision function $d(\bm{x})$ can be defined for every pixel $\bm{x}$ of the corresponding object image, therefore we interpret it as an image and we call it \emph{SVS image}.

@@

\subsubsection*{Non-rigid ICP and Correspondence Basis Creation} \label{sec:trabasis}

@@

\subsubsection*{Variational Shape Flow Estimation}%{Multi-image Subspace Flow}
\label{varshapeflow}

@@

Figure~\ref{fig:deformationfield} shows some examples of deformation fields derived from the estimated shape flow computed by the aforementioned method. These results correspond to exemplar training shapes in the case of an arm dataset.

@@

\begin{figure}[b!]
    \centering
    \includegraphics[width=0.45\textwidth]{resources/models}
    \caption{Exemplar dense shape models build for faces and ears. Dense shapes are presented as grid for better visualisation.}
    \label{fig:dense_models}
\end{figure}
